Comparing software variability across and within fMRI analysis packages

### 2022-01-02 paper/paper.tex
Minor edits on method

We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. These
values were chosen such that the numerical perturbation simulates machine
error. The resulting samples are equally plausible estimates of
the true
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
numerical result at the precision used by the pipelines. Moreover, to evaluate numerical perturbations at different magnitudes,
we repeated the FSL analyses for virtual
precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
and double-precision values. We also repeated the FSL analyses for virtual
precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
set the virtual precision to $t=24$~bits for single-precision values.

>>>>

We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. These
values were chosen such that the numerical perturbation simulates machine
error. The resulting samples are equally plausible estimates of
the true numerical result at the precision used by the pipelines. 
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
% Moreover, to evaluate numerical perturbations at different magnitudes,
% we repeated the FSL analyses for virtual
% precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
% and double-precision values. We also repeated the FSL analyses for virtual
% precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
% set the virtual precision to $t=24$~bits for single-precision values.
